\input{header.tex}

\title{Solutions Sheet 8}
\author{Yannis B\"{a}hni}
\address[Yannis B\"{a}hni]{University of Zurich, R\"{a}mistrasse 71, 8006 Zurich}
\email[Yannis B\"{a}hni]{\href{mailto:yannis.baehni@uzh.ch}{yannis.baehni@uzh.ch}}

\begin{document}
\maketitle
\thispagestyle{fancy}
\begin{enumerate}[label = \textbf{Exercise \arabic*.},wide = 0pt, itemsep=1.5ex]
	\item Let $U := \mathbb{C} \setminus \cbr[0]{\pm e^{\pm i\pi/4}}$ and define $F: U \to \mathbb{C}$ by
		\begin{equation}
			F(z) := \frac{1}{1 + z^4}.	
		\end{equation}
		Clearly $F \in \mathcal{O}(U)$ as a well defined rational function, $U$ is open in $\mathbb{C}$ and $\mathbb{R} \subseteq U$. Furthermore $F\vert_\mathbb{R} = f$. Hence $F$ is a holomorphic continuation of $f$. Since having an analytic continuation is equivalent to be real-analytic (see \cite[100]{fischer2003funktionentheorie}), we have that $f$ is real-analytic.\\
		Let $x_0 \in \mathbb{R}$. The Taylor series expansion of $f$ is completely determined by the one of $F$. This is due to the fact, that $F^{(\nu)}(x_0) = f^{(\nu)}(x_0)$ for all $\nu \in \mathbb{N}_0$. By Cauchy-Taylor, $F$ is expandable into a power series in the largest ball around $x_0$ contained in $U$, i.e. 
		\begin{equation}
			F(z) = \sum_{\nu = 0}^\infty a_\nu(z - x_0)^\nu
			\label{eq:expansion}
		\end{equation}
		\noindent and the convergence is normal there. Thus the radius of convergence $R$ of the expansion (\ref{eq:expansion}) is at least $\abs[0]{x_0 - e^{i\pi/4}}$ if $x_0 \geq 0$ and $\abs[0]{x_0 + e^{i\pi/4}}$ if $x_0 \leq 0$. Let $r:= \abs[0]{x_0 - e^{i\pi/4}}$ and assume $x_0 \geq 0$ (the case $x_0 \leq 0$ is similar). Furthermore assume that $R > r$. Hence the series expansion (\ref{eq:expansion}) converges in $B_R(x_0)$ and therefore defines a function $G: B_R(x_0) \to \mathbb{C}$ by
		\begin{equation}
			G(z) := \sum_{\nu = 0}^\infty a_\nu(z - x_0)^\nu 
		\end{equation}
		\noindent with $G\vert_{B_r}(x_0) = F$. Since $G$ is expandable in a power series, we have $G \in \mathcal{O}(B_R(x_0))$ by \cite[187]{remmert2002funktionentheorie}. Since any holomorphic function is continuous, we have $G \in \mathscr{C}(B_R(x_0))$. Let $(z_\nu)_{\nu \in \mathbb{N}}$ be a sequence in $B_r(x_0)$ such that $\lim_{\nu \to \infty} z_\nu = e^{i\pi/4}$. Clearly
		\begin{equation}
			\lim_{\nu \to \infty}F(z_\nu) = \infty
		\end{equation}
		\noindent and since $G\vert_{B_r(x_0)} = F$ we have
		\begin{equation}
			\lim_{\nu \to \infty} G(z_\nu) = \infty.	
		\end{equation}
		\noindent But since $R > r$, $G$ is continuous at $e^{i\pi/4}$ and so we must have
		\begin{equation}
			G(e^{i\pi/4}) = \lim_{\nu \to \infty}G(z_\nu) = \infty.
		\end{equation}
		Thus the series $G$ diverges at $e^{i\pi/4}$, contradicting that $e^{i\pi/4} \in B_R(x_0)$. In conclusion 
		\begin{equation}
			\boxed{R(x_0) = \min\del[0]{\abs[0]{x_0 - e^{i\pi/4}},\abs[0]{x_0 + e^{i\pi/4}}} \qquad x_0 \in \mathbb{R}.}
		\end{equation}

	\item
		Since $f \in \mathcal{O}(\mathbb{E})$ we have that $f \in \mathscr{C}(\mathbb{E})$. Thus since $\partial B_r(0)$, $0 \leq r < 1$, is compact we have that $\abs{f}$ attains its supremum on $\partial B_r(0)$. Hence we have 
				\begin{equation}
					M(r) = \max_{\abs[0]{z} = r} \abs[0]{f(z)}
				\end{equation}
				\noindent and actually $M: \intco{0,1} \to \mathbb{R}_{\geq 0}$.
		\begin{enumerate}[label = (\roman*),wide = 0pt, itemsep=1.5ex]
			\item Let $0 < R < 1$. Since $\overline{B_R}(0)$ is compact and $f \in \mathscr{C}(\mathbb{E})$, we have that $f$ is uniformly continuous on $\overline{B_R}(0)$ (see for example \cite[138]{alt2016linear} or \cite[215]{lee:topological_manifolds:2011}). By the reversed triangle inequality, also $\abs[0]{f}$ is uniformly continuous on $\overline{B_R}(0)$. 
				\begin{proposition}
					$M$ is uniformly continuous on $\intcc{0,R}$, $0 < R < 1$.
					\label{prop:M_uniform}
				\end{proposition}

				\begin{proof}
					Fix $0 < R < 1$ and let $\varepsilon > 0$. Since $\abs[0]{f}$ is uniformly continuous on $\overline{B_R}(0)$, we find $\delta > 0$ such that for all $z_1,z_2 \in \overline{B_R}(0)$, $\abs[0]{z_1 - z_2} < \delta$ implies $\abs[0]{\abs[0]{f(z_1)} - \abs[0]{f(z_2)}} < \varepsilon$. Let $r_1,r_2 \in \intcc{0,R}$. There are two cases to distinguish. First assume $M(r_1) \geq M(r_2)$. We find $\varphi_1 \in \mathbb{R}$ such that $M(r_1) = \abs[0]{f(r_1e^{i\varphi_1})}$. If $\abs[0]{r_1 - r_2} = \abs[0]{r_1e^{i\varphi_1} - r_2e^{i\varphi_1}} < \delta$, we have that
				\begin{equation}
					M(r_1) - M(r_2) \leq M(r_1) - \abs[0]{f(r_2e^{i\varphi_1})} = \abs[0]{f(r_1e^{i\varphi_1})} - \abs[0]{f(r_2e^{i\varphi_1})} < \varepsilon
				\end{equation}
				\noindent since $r_1e^{i\varphi_1},r_2e^{i\varphi_1} \in \overline{B_R}(0)$. Now assume $M(r_1) \leq M(r_2)$. Again, we find $\varphi_2 \in \mathbb{R}$ such that $M(r_2) = \abs[0]{f(r_2 e^{i\varphi_2})}$ and analogously if $\abs[0]{r_1 - r_2} = \abs[0]{r_1e^{i\varphi_2} - r_2e^{i\varphi_2}} < \delta$, we have that
				\begin{align*}
					M(r_2) - M(r_1) \leq M(r_2) - \abs[0]{f(r_1e^{i\varphi_2})} = \abs[0]{f(r_2e^{i\varphi_2})} - \abs[0]{f(r_1e^{i\varphi_2})} < \varepsilon
				\end{align*}
				\noindent since $r_1e^{i\varphi_2},r_2e^{i\varphi_2} \in \overline{B_R}(0)$. In conclusion $\abs[0]{M(r_1) - M(r_2)} < \varepsilon$ whenever $\abs[0]{r_1 - r_2} < \delta$. Hence $M$ is uniformly continuous on $\intcc{0,R}$.
				\end{proof}

				\begin{corollary}
					$M \in \mathscr{C}(\intco{0,1})$.
				\end{corollary}
				\begin{proof}
					By proposition \ref{prop:M_uniform}, $M \in \mathscr{C}(\intcc{0,R})$ for any $0 < R < 1$ since uniform continuity implies continuity. Let $r_0 \in \intco{0,1}$. We find $0 \leq r_0 < R < 1$ and since continuity is a local property, we have that $M$ is continuous at $r_0$. Since the choice of $r_0$ was arbitray, we conclude that $M \in \mathscr{C}(\intco{0,1})$.
				\end{proof}
 
				\begin{lemma}
					$M$ is nondecreasing.
				\end{lemma}
				\begin{proof}
					Let $0 \leq r_1 < r_2 < 1$. We have $\overline{B_{r_2}}(0) \subseteq \mathbb{E}$. Thus $f$ is holomorphic in the bounded domain $B_{r_2}(0)$ and continuous on $\overline{B_{r_2}}(0)$. The maximum modulus principle \cite[91]{fischer2003funktionentheorie} implies 
				\begin{equation}
					\abs[0]{f(z)} \leq \max_{\zeta \in \partial B_{r_2}(0)}\abs[0]{f(\zeta)} = M(r_2)
				\end{equation}
				\noindent for all $z \in \overline{B_{r_2}}(0)$. In particular 
				\begin{equation}
					M(r_1) = \max_{\zeta \in \partial B_{r_1}(0)}\abs[0]{f(\zeta)} \leq \max_{\zeta \in \partial B_{r_2}(0)}\abs[0]{f(\zeta)} = M(r_2).
				\end{equation}
				Thus $M$ is nondecreasing.
				\end{proof}

			\item Proof by contradiction. Assume that $f$ is not constant and that $M$ is not increasing. Hence we find $0 \leq r_1 < r_2 < 1$ such that $M(r_1) = M(r_2)$, since by part (i) we already know that $M$ is nondecreasing. We find $z_0 \in \partial B_{r_1}(0)$ such that $M(r_1) = \abs[0]{f(z_0)}$. An application of the maximum principle similar to part (i) yields
				\begin{equation}
					\abs[0]{f(z)} \leq \max_{\zeta \in \partial B_{r_2}(0)}	\abs[0]{f(\zeta)} = M(r_2) = M(r_1) = \abs[0]{f(z_0)}
					\label{eq:max}
				\end{equation}
				\noindent for all $z \in \overline{B_{r_2}}(0)$. Define $r := \min(r_1,r_2 - r_1)$. Since $B_r(z_0) \neq \cbr[0]{z_0}$, $B_r(z_0) \subseteq B_{r_2}(0)$ and by (\ref{eq:max}) we have that $\abs[0]{f(z)} \leq \abs[0]{f(z_0)}$ for all $z \in B_r(0)$, $\abs[0]{f}$ has a local maximum at $z_0 \in B_{r_2}(0)$. Thus by the maximum modulus principle, $f$ is constant in $B_{r_2}(0)$. Since $0 < r_2$, $B_{r_2}(0)$ is not discrete in $\mathbb{E}$, hence if we define $g: \mathbb{E} \to \mathbb{C}$ by $g(z) := f(z_0)$, clearly $g \in \mathcal{O}(\mathbb{E})$ and $f = g$ on $B_{r_2}(0)$. Hence by the second version of the identity principle \cite[85]{fischer2003funktionentheorie} we have $f = g$ on $\mathbb{E}$ which implies that $f$ is constant on $\mathbb{E}$. Contradiction. 
		\end{enumerate}

	\item Proof by contradiction. Since no point $\zeta \in \partial B_R(z_0)$ is singular, we find a neighbourhood $U_\zeta$ of $\zeta$ and a function $f_\zeta \in \mathcal{O}(U_\zeta)$, such that 
		\begin{equation}
			f_\zeta(z) = \sum_{\nu = 0}^\infty a_\nu(z - z_0)^\nu
		\end{equation}
		\noindent for all $z \in U_\zeta \cap B_R(z_0)$. Since each $U_\zeta$ contains an open set containing $\zeta$, we find $r_\zeta$, such that $B_{r_\zeta}(\zeta) \subseteq U_\zeta$. Therefore we have that
		\begin{equation}
			\partial B_R(z_0) \subseteq \bigcup_{\zeta \in \partial B_R(z_0)} B_{r_\zeta}(\zeta)
		\end{equation}
		\noindent is an open cover of $\partial B_R(z_0)$. Since $\partial B_R(z_0)$ is compact, we find $\zeta_1,\dots,\zeta_n$ such that $B_{r_{\zeta_1}}(\zeta_1),\dots,B_{r_{\zeta_n}}(\zeta_n)$ still covers $\partial B_R(z_0)$. The next step is conceptually easy, but notationally ugly. We will explain it in a quite informal way. Now the intersection $B_{r_{\zeta_\nu}}(\zeta_\nu) \cap B_{r_{\zeta_\mu}}(\zeta_\mu)$ is open and thus if $B_{r_{\zeta_\nu}}(\zeta_\nu) \cap B_{r_{\zeta_\mu}}(\zeta_\mu) \neq \varnothing$, we find an open ball contained in the intersection $B_{r_{\zeta_\nu}}(\zeta_\nu) \cap B_{r_{\zeta_\mu}}(\zeta_\mu) \neq \varnothing$. Taking the minimum of all radii of those balls lying in the intersection (this is possible since there are only finitely many ones), we find $\hat{R} > R$ such that
		\begin{equation}
			\partial B_{\hat{R}}(z_0) \subseteq \bigcup_{k = 1}^n B_{r_{\zeta_k}}(\zeta_k).
		\end{equation}
		Next we construct a function $g: B_{\hat{R}}(z_0) \to \mathbb{C}$. Define $g(z) := \sum_{\nu = 0}^\infty a_\nu (z - z_0)^\nu$ if $z \in B_R(z_0)$. If $z \in \del[0]{B_{r_{\zeta_\nu}}(\zeta_\nu) \cap B_{r_{\zeta_\mu}}(\zeta_\mu)} \setminus B_R(z_0)$, we have that $f_{\zeta_\nu} = f_{\zeta_\mu}$ in $B_{r_{\zeta_\nu}}(\zeta_\nu) \cap B_{r_{\zeta_\mu}}(\zeta_\mu) \cap B_R(z_0)$, which is open and therefore not discrete in $B_{r_{\zeta_\nu}}(\zeta_\nu) \cap B_{r_{\zeta_\mu}}(\zeta_\mu)$. Thus by the second version of the identity principle we have $f_{\zeta_\nu} = f_{\zeta_{\mu}}$ on $B_{r_{\zeta_\nu}}(\zeta_\nu) \cap B_{r_{\zeta_\mu}}(\zeta_\mu)$. Therefore $g(z) := f_{\zeta_{\nu}}(z) = f_{\zeta_\mu}(z)$ is well defined. In the remaining cases, define $g(z) := f_{\zeta_\nu}(z)$ if $z \in B_{r_{\zeta_\nu}}(\zeta_\nu)$. Since $f_{\zeta_\nu} \in \mathcal{O}(U_{\zeta_\nu})$ and by the theorem on interchangeability of differentiation and summation we have that any power series is holomorphic within its radius of convergence, we have that $g \in \mathcal{O}(B_{\hat{R}}(z_0))$. An application of Cauchy-Taylor yields
		\begin{equation}
			g(z) = \sum_{\nu = 0}^\infty \frac{g^{(\nu)}(z_0)}{\nu !}(z - z_0)^\nu = \sum_{\nu = 0}^\infty \frac{f^{(\nu)}(z_0)}{\nu !}(z - z_0)^\nu
		\end{equation}
		\noindent for all $z \in B_{\hat{R}}(z_0)$ since $g = f$ on $B_R(z_0)$. Furthermore, since $\hat{R} > R$ we have that $\sum_{\nu = 0}^\infty a_\nu(z - z_0)^\nu$ is convergent in $B_{\hat{R}}(z_0) \setminus \overline{B_R}(z_0)$, contradicting that $\sum_{\nu = 0}^\infty a_{\nu} (z - z_0)^\nu$ is divergent there by the definition of the radius of convergence. Contradiction.

	\item Central is Weierstrass' differentiation theorem for compact convergent series. For each $\nu \in \mathbb{N}_0$ let
		\begin{equation}
			f_\nu(z) := \sum_{\mu = 0}^\infty c_{\nu \mu}(z - z_0)^\mu
		\end{equation}
		\noindent be convergent in $B_r(z_0)$, $r > 0$, $z_0 \in \mathbb{C}$. Furthermore, assume that
		\begin{equation}
			f(z) := \sum_{\nu = 0}^\infty f_\nu(z) = \sum_{\nu = 0}^\infty \sum_{\mu = 0}^\infty c_{\nu \mu}(z - z_0)^\mu
		\end{equation}
		\noindent is normally convergent in $B_r(z_0)$. Since $r > 0$, the theorem on interchangeability of differentiation and summation of power series implies that $f_\nu \in \mathcal{O}(B_r(z_0))$ for all $\nu \in \mathbb{N}_0$. Since $\sum_{\nu = 0}^\infty f_\nu$ is normally convergent in $B_r(z_0)$, we have that $\sum_{\nu = 0}^\infty f_\nu$ is locally uniformly convergent in $B_r(z_0)$ and thus compactly convergent in $B_r(z_0)$. Hence Weierstrass' theorem implies that the limit function $f$ is holomorphic in $B_r(z_0)$. Thus by the expansion theorem of Cauchy-Taylor, for any $z \in B_r(z_0)$ we find a disc centered at $z$ where $f$ is expandable in a Taylor seriers. This implies that $f$ is analytic in $B_r(z_0)$. Furthermore, the same theorem implies that for any $k \in \mathbb{N}_0$ we have
		\begin{equation}
			f^{(k)}(z) = \sum_{\nu = 0}^\infty f_\nu^{(k)}(z) = \sum_{\nu = 0}^\infty \sum_{\mu = k}^\infty k! {\mu \choose k}c_{\nu \mu}(z - z_0)^{\mu - k} 
		\end{equation}
		\noindent for all $z \in B_r(z_0)$ by the theorem on interchangeability of differentiation and summation of power series. Since $f \in \mathcal{O}(B_r(z_0))$, the expansion theorem of Cauchy-Taylor implies that 
		\begin{equation}
			f(z) = \sum_{k = 0}^\infty \frac{f^{(k)}(z_0)}{k !} (z - z_0)^k = \sum_{k = 0}^\infty \del[4]{\sum_{\nu = 0}^\infty c_{\nu k}} (z - z_0)^k
		\end{equation}
		\noindent for all $z \in B_r(z_0)$.
\end{enumerate}
%\originalsectionstyle
\printbibliography
\end{document}
